Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-26 prop_letter.tex
prop_letter.tex Fix some typos and citations...

We conclude this section with a generalization of expectation values
of observables in the context of QIVPMs. In conventional quantum
mechanics the expectation value of an observable as defined in
Eq.~(\eqref{eq:quantum-expectation}) is a unique real number. The
generalization to QIVPMs implies that this expectation value will
itself become bounded by an interval.

@@

Our generalization of quantum probability measures to QIVPMs allows us
to strengthen the scope of one of the fundamental theorems of quantum
information: the Kochen-Specker
theorem~\cite{PeresRon1988,peres1995quantum}. Our finite-precision
extension of the theorem will suggest a resolution to the debate
initiated by Meyer and Mermin on the relevance of the Kochen-Specker
to experimental, and hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated under
the assumption that all observables of a quantum mechanical system
have \emph{definite values at all times}~\cite{Held2016}. Our
interval-valued probability framework will allow us to state, and
prove, a stronger version of the theorem that holds even if the
observables have values that are only definite up to some specific
parameter that quantifies experimental uncertainty. Put differently,
our stronger statement and theorem quantifies Mermin's intuition:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case~\citep{Mermin1999}.
\end{quote}

>>>>

We conclude this section with a generalization of expectation values
of observables in the context of QIVPMs. In conventional quantum
mechanics the expectation value of an observable as defined in
Eq.~\eqref{eq:quantum-expectation} is a unique real number. The
generalization to QIVPMs implies that this expectation value will
itself become bounded by an interval.

@@

Our generalization of quantum probability measures to QIVPMs allows us
to strengthen the scope of one of the fundamental theorems of quantum
information: the Kochen-Specker
theorem~\cite{PeresRon1988,peres1995quantum}. Our finite-precision
extension of the theorem will suggest a resolution to the debate
initiated by Meyer and Mermin on the relevance of the Kochen-Specker
to experimental, and hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated under
the assumption that all observables of a quantum mechanical system
have \emph{definite values at all times}~\cite{Held2016}. Our
interval-valued probability framework will allow us to state, and
prove, a stronger version of the theorem that holds even if the
observables have values that are only definite up to some specific
parameter that quantifies experimental uncertainty. Put differently,
our stronger statement and theorem quantifies Mermin's
intuition~\citep{Mermin1999}:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case.
\end{quote}
